Analytic Doppler Imaging

### 2019-08-08 tex/gitlinks.tex
added vogtstar fig

\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/b9ff114beba2d54f032d05754e1d62ef624acd09/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/b9ff114beba2d54f032d05754e1d62ef624acd09/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/b9ff114beba2d54f032d05754e1d62ef624acd09/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

>>>>

\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/4e5cae5dc1b1284c9989d7eb27427acca7088476/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/4e5cae5dc1b1284c9989d7eb27427acca7088476/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/4e5cae5dc1b1284c9989d7eb27427acca7088476/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
